\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-01-08 archive.tex
random/cherry split for dreams

Procedural visual concepts are studied across AI and cognitive science
--- Bongard problems~\cite{Moscow}, Raven's progressive
matrices~\cite{raven2003raven}, and Lake et al.'s BPL model of
omniglot~\cite{lake2015human} are prominent examples.  Here we take
inspiration from LOGO Turtle graphics~\cite{turtle}, and give our
agent the ability to control a pen, along with arithmetic operations
on angles and distances and simple control flow primitives.  We task
it with drawing a small corpus of images starting from this basis.

@@

    \\\bottomrule 
  \end{tabular}
  \caption{Example primitives learned by \system when trained on tasks in Figure~\ref{everyLogo}. Agent learns parametric routines for drawing families of curves (left) as well as subroutines that take entire programs as input (right). Each row of images on the left is the same code executed with different parameters. Each image on the right is the same code executed with different parameters and with a different subprogram provided as input.}\label{logoPrimitives}
  \end{figure}
\begin{figure}
\centering  \begin{tabular}{c|c}
      \includegraphics[width = 0.5\textwidth]{figures/initialDreams/montage.png}&
  \includegraphics[width = 0.5\textwidth]{figures/finalDreams/montage.png}
    \end{tabular}
  \caption{Dreams, or samples, from the DSL before (left) and after (right) training on tasks in Figure~\ref{everyLogo}. Blue: where the agent started drawing. Pink: where the agent ended drawing.}\label{logoDreams}
\end{figure}

>>>>

Procedural visual concepts are studied across AI and cognitive science
--- Bongard problems~\cite{Moscow}, Raven's progressive
matrices~\cite{raven2003raven}, and Lake et al.'s BPL model of
omniglot~\cite{lake2015human} are prominent examples.  Here we take
inspiration from LOGO Turtle graphics~\cite{turtle}, tasking it with
drawing a modest corpus of images while equipping it with control over
a `pen', along with arithmetic operations on angles and distances.

@@

    \\\bottomrule 
  \end{tabular}
  \caption{Example primitives learned by \system when trained on tasks in Figure~\ref{everyLogo}. Agent learns parametric routines for drawing families of curves (left) as well as subroutines that take entire programs as input (right). Each row of images on the left is the same code executed with different parameters. Each image on the right is the same code executed with different parameters and with a different subprogram provided as input.}\label{logoPrimitives}
  \end{figure}
\begin{figure}
\centering  \begin{tabular}{c|cc}
  \begin{tabular}{c}
    \includegraphics[width = 0.45\textwidth]{figures/initialDreams/montage.png}
    \end{tabular}&
      \begin{tabular}{c}
        \includegraphics[width = 0.45\textwidth]{figures/finalDreams/cherry_random_montage.png}
        \end{tabular}&
      \rotatebox[origin=c]{90}{Cherry picked\hspace{3cm}Random}
    \end{tabular}
  \caption{Sixteen dreams, or samples, from the DSL before (left) and after (right) training on tasks in Figure~\ref{everyLogo}. Blue: where the agent started drawing. Pink: where the agent ended drawing.}\label{logoDreams}
\end{figure}
